Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-08-17 EMNLP-demo-paper/result.tex
minor fix in result

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea". However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction. The grammatical structure is visually shown in the form of the dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two ``greens" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

>>>>

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pair (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea." However, these two \emph{greens} modify different nouns, which potentially leads to the wrong prediction. The grammatical structure is visually shown in the form of the dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not have access to the syntactic information and mistakenly assumes the two \emph{greens} modify the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two ``greens" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).
